### 2021-05-18 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   experiments.tex   new file:   picture/picture4.key   modified:   picture/picture4.pdf
modified:   conclusion.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   modified:   paper.tex   new file:   paper.ver06.appendix.pdf   new file:   paper.ver06.pdf   modified:   picture/picture4.key   modified:   picture/picture4.pdf

The fouth one, \emph{pretrained model based joint text classification and NER model}. 
We choose the work from \cite{chen2019bert} as our baseline system, which utilizes a strong RoBERTa-large model to jointly train two losses.
Our SFC framework is also conveniently supportive of extra NER loss that in stage 1 a fourth task with a NER loss is trivially derived based on the output states from a pretrained model.

@@

All setting details can be found in the appendix due to the space limitation.

@@

\begin{table}
  \begin{centering}
    \scalebox{0.85}{
      \begin{tabular}{|c|c|c|c|}
        \hline
        F1 score & 2-stage SFC & joint SFC & Gap \tabularnewline
        \hline
        top-1 accuracy & \textbf{81.50} & 81.07 & -0.47 \tabularnewline
        top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 \tabularnewline
        \hline
      \end{tabular}
    }
    \par
  \end{centering}
  \caption{The average classification accuracy in percentage in stage 1 on all five dataset.}
  \label{tbe:top1_5_accuracy}
\end{table}

@@

\subsection{Settings of hyperparameters} 
In Table \ref{tbe:table3}, we explore the influence from hyperparameters on ITG and Amazon-670K datasets. 
We control the total number of sampled sentence pairs to about 50 to 60, and obatin about five combinations of hyperparameters.

We find that the best setting of hyperparameters is different with different datasets. 
The class label number of ITG and Amazon-670k are similar in our experiments, around 250. 
However the number of data points in ITG is approximately 2 times as many as that in Amazon-670k.
Therefore, the setting of $K=5$ and $P=10$ is good enough for ITG since most of the classes contains over 10 data points. 
However, in Amazon-670k, the data per each class is scarce, and, we may need more candidate classes to sample enough effective sentence pairs for the stage 2 traininig of SFC. 
Thus, the setting of $K=10$ and $P=5$ becomes a good choice.

>>>>

The fourth one, \emph{pretrained model based joint text classification and NER model}. 
We choose the work from \cite{chen2019bert} as our baseline system, which utilizes a strong RoBERTa-large model to jointly train two losses.
Our SFC framework is also conveniently supportive of extra NER loss that in stage 1 a fourth task with a NER loss is trivially derived based on the output states from a pretrained model.

@@

@@

\begin{table}
  \begin{centering}
    \scalebox{0.85}{
      \begin{tabular}{|c|c|c|c|}
        \hline
        F1 score & 2-stage SFC & joint SFC & Gap \tabularnewline
        \hline
        top-1 accuracy & \textbf{81.50} & 81.07 & -0.47 \tabularnewline
        top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 \tabularnewline
        \hline
      \end{tabular}
    }
    \par
  \end{centering}
  \caption{The average classification accuracy in percentage in stage 1 on the first five datasets.}
  \label{tbe:top1_5_accuracy}
\end{table}

@@

\subsection{Settings of hyperparameters} 
In Table \ref{tbe:table3}, we explore the influence from hyperparameters on ITG and Amazon-670K datasets. 
We control the total number of sampled sentence pairs to about 50 to 60, and obtain about five combinations of hyperparameters.

We find that the best setting of hyperparameters is different with different datasets. 
The class label number of ITG and Amazon-670k are similar in our experiments, around 250. 
However the number of data points in ITG is approximately 2 times as many as that in Amazon-670k.
Therefore, the setting of $K=5$ and $P=10$ is good enough for ITG since most of the classes contains over 10 data points. 
However, in Amazon-670k, the data per each class is scarce, and, we may need more candidate classes to sample enough effective sentence pairs for the stage 2 training of SFC. 
Thus, the setting of $K=10$ and $P=5$ becomes a good choice.

### 2021-05-18 chatbot_classification/03.emnlp_2021/introduction.tex
modified:   conclusion.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   modified:   paper.tex   new file:   paper.ver06.appendix.pdf   new file:   paper.ver06.pdf   modified:   picture/picture4.key   modified:   picture/picture4.pdf

Task-specific conversational chatbot \cite{wen2016network} has been applied into many practical products. 
A popular one is the smart speaker, e.g. Alex, Siri, Google home. 
Another important one is the customer service system, which greatly help human agents handle miscellanious customer's questions.
No matter these applications involves single- or multi-round conversations, a critical step is to identify the intent behind a user's question or response. 
The detected intent with its associated attributes is then mapped into a predefined dialog logic to obtain a suitable response to return to customers.

@@

Existent approaches for intent detection can be roughly categorized as text classfication model and text similarity model.

The first one, \emph{text classification model}, includes a variety of work.
From traditional machine learning models like SVM \cite{suykens1999least}, boosting tree \cite{tu2005probabilistic}, to neural networks \cite{wen2016network}, such as convolutional neural networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very} and long short term memory networks (LSTMs) \cite{mousa2017contextual,liu2016recurrent}, and then to the most popular pretrained language models based, such as BERT \cite{devlin2018bert}, RoBERTa \cite{liu2019roberta} and etc. 
Especiallaly, pretrained models based \cite{vaswani2017attention} tends to be more helpful in the few-shot scenario \cite{yu2018diverse, madabushi2020cost} to alleviate the dearth of training data.
Another two interesting lines of work, label-word joint models, and joint NER and classification are discussed in the related work of appendix.

@@

Despite plenty of success of these two methodologies, they still have some limitations in this task especially when data is insufficient.
Regarding the \emph{text classification model}, it learns a function that directly maps an input query into its expected label.
Its training requires data in the form of a pair of a query and a task dependent label. 
It is quite hard to adopt labeled data from other domains, as their label definitions are often incompatible to each other. 
Though we can use some data augmentation methods to alleivate the paucity of data, e.g., translation based paraphrasing methods, the resulting benefit is still limited because of the data being homogeneous, in the case that our labeled data is very insufficient.
Regarding the \emph{similarity model}, the foremost advantage is it does not pose any restriction on the label definition of user intents, but aims to learn a function that measure how similar of two sentences are. 
Then in the intent detection task, we are only concerned which labeled query is the most similary one to the current input, and then use its label as the output.
This results in a possibility that even though the labeled data in current domain is scarce, we may borrow additional data from another domain to help enhance the similarity model to make a better intent prediction.
Nevertheless, just as every coin has two sides, the high flexibility of similarity model leads to its worse performance compared to a classification model, because its training loss differs from a classification loss corresponding to the intent detection goal.
More, it requires an auxiliary model to narrow down candidate labeled queries to speed up the calculation, which makes it slow in the speed and tricky in the auxiliary model selection.

The above limitations motivate us to propose a system that may take both the high performance from a classification model and the ability of supporting out-of-domain data from a similarity model.
We call our system as SFC, short for similarity model fused with classification model, shown in Fig. \ref{fig:framework}. 
In order to train effectively, we further borrow the multi-task learning \cite{caruana1993multitask,collobert2008unified, liu2019multi}.
Our basic idea come naturally, and the first impementation consists of two stages. 
In the first stage, we use an auxiliary model to select top-K most possible labels for an input. 
This model can be an elastic search \cite{divya2013elasticsearch} or a text classification model trained on current domain. 
In the second stage, we build a classification model which is composed of several similarity modules. 
Then, this structure derives two goals to train towards, the task-specific classification loss , and the similarity loss on both in-domain and out-of-domain data. 
In this version, the two stages are independently optimized, so we call it \emph{2-stage SFC}.

@@

Since SFC is in the framework of multi-task training, its inheriently supports adding additional tasks, such as NER, to gain further improvement.

>>>>

Task-specific conversational chatbot \cite{wen2016network} has been applied into many practical products. 
A popular one is the smart speaker, e.g. Alex, Siri, Google home. 
Another important one is the customer service system, which greatly help human agents handle miscellaneous customer's questions.
No matter these applications involves single- or multi-round conversations, a critical step is to identify the intent behind a user's question or response. 
The detected intent with its associated attributes is then mapped into a predefined dialog logic to obtain a suitable response to return to customers.

@@

Existent approaches for intent detection can be roughly categorized as text classification model and text similarity model.

The first one, \emph{text classification model}, includes a variety of work.
From traditional machine learning models like SVM \cite{suykens1999least}, boosting tree \cite{tu2005probabilistic}, to neural networks \cite{wen2016network}, such as convolutional neural networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very} and long short term memory networks (LSTMs) \cite{mousa2017contextual,liu2016recurrent}, and then to the most popular pretrained language models based, such as BERT \cite{devlin2018bert}, RoBERTa \cite{liu2019roberta} and etc. 
Especially, pretrained models based \cite{vaswani2017attention} tends to be more helpful in the few-shot scenario \cite{yu2018diverse, madabushi2020cost} to alleviate the dearth of training data.
Another two interesting lines of work, label-word joint models, and joint NER and classification are discussed in the related work of appendix.

@@

Despite plenty of success of these two methodologies, they still have some limitations in this task especially when data is insufficient.
Regarding the \emph{text classification model}, it learns a function that directly maps an input query into its expected label.
Its training requires data in the form of a pair of a query and a task dependent label. 
It is quite hard to adopt labeled data from other domains, as their label definitions are often incompatible to each other. 
Though we can use some data augmentation methods to alleviate the paucity of data, e.g., translation based paraphrasing methods, the resulting benefit is still limited because of the data being homogeneous, in the case that our labeled data is very insufficient.
Regarding the \emph{similarity model}, the foremost advantage is it does not pose any restriction on the label definition of user intents, but aims to learn a function that measure how similar of two sentences are. 
Then in the intent detection task, we are only concerned which labeled query is the most similar one to the current input, and then use its label as the output.
This results in a possibility that even though the labeled data in current domain is scarce, we may borrow additional data from another domain to help enhance the similarity model to make a better intent prediction.
Nevertheless, just as every coin has two sides, the high flexibility of similarity model leads to its worse performance compared to a classification model, because its training loss differs from a classification loss corresponding to the intent detection goal.
More, it requires an auxiliary model to narrow down candidate labeled queries to speed up the calculation, which makes it slow in the speed and tricky in the auxiliary model selection.

The above limitations motivate us to propose a system that may take both the high performance from a classification model and the ability of supporting out-of-domain data from a similarity model.
We call our system as SFC, short for similarity model fused with classification model, shown in Fig. \ref{fig:framework}. 
In order to train effectively, we further borrow the multi-task learning \cite{caruana1993multitask,collobert2008unified, liu2019multi}.
Our basic idea come naturally, and the first implementation consists of two stages. 
In the first stage, we use an auxiliary model to select top-K most possible labels for an input. 
This model can be an elastic search \cite{divya2013elasticsearch} or a text classification model trained on current domain. 
In the second stage, we build a classification model which is composed of several similarity modules. 
Then, this structure derives two goals to train towards, the task-specific classification loss , and the similarity loss on both in-domain and out-of-domain data. 
In this version, the two stages are independently optimized, so we call it \emph{2-stage SFC}.

@@

Since SFC is in the framework of multi-task training, its inherently supports adding additional tasks, such as NER, to gain further improvement.

### 2021-05-18 chatbot_classification/03.emnlp_2021/methodology.tex
modified:   conclusion.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   modified:   paper.tex   new file:   paper.ver06.appendix.pdf   new file:   paper.ver06.pdf   modified:   picture/picture4.key   modified:   picture/picture4.pdf

\subsection{Joint SFC}
In 2-stage SFC, two stages are separate that there is no deep interaction with each other during training. 
In this case, the performance of stage 1 may limit the model potential in stage 2; 
meanwhile, stage 2 also cannot loop feedback back to stage 1 in trainig for improvement. 
Therefore, we propose to jointly train all stages, shown in Fig. \ref{fig:framework}.

>>>>

\subsection{Joint SFC}
In 2-stage SFC, two stages are separate that there is no deep interaction with each other during training. 
In this case, the performance of stage 1 may limit the model potential in stage 2; 
meanwhile, stage 2 also cannot loop feedback back to stage 1 in training for improvement. 
Therefore, we propose to jointly train all stages, shown in Fig. \ref{fig:framework}.
